Conoco Phillips 2020

### 2020-06-02 CP_2020.Rmd
updated example; updated bootstrap; fixed some references; still need to do more

```{r}
## September 11th (no trading from T-F); 1 day nowcast
COP_close <- COP %>% select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
GSPC_close <- GSPC %>% select(GSPC.Close, Date) %>% 
  rename(GSPC_Close = GSPC.Close)
COP_close <- merge(COP_close, GSPC_close)
COP_close <- merge(COP_close, WTI_Crude)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start <- which(COP_close$Date == "2001-09-10")
start_day <- as.numeric(1:nrow(COP_close) == start + 1)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
alpha_9_11
```

@@

The first 4 major shocks of 2008 were proceeded by unprecedented failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike. The March 8th, September 12th, and September 26th shock effects were proceeded by the bailouts or failures of Bear Stearns, Lehman Brothers, and Washington Mutual financial institutions. The September 8th shock effect was proceeded by Fannie Mae and Freddie Mac being placed in conservatorship.

We first find the Baer Stearns shock effect. Here is the estimated shock effect 1 day in the future with covariates:

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2008-03-18")
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
m_COP_3_18 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_3_18 <- summary(m_COP_3_18)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_3_18
```

@@

```{r}
m_COP_3_18_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_3_18_no <- summary(m_COP_3_18_no)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_3_18_no
```

```{r}
COP_close <- COP_close %>% select(-"start_day")
COP_close[which(COP_close$COP_Close - COP_close$Y >= 3.5), ][2:4, ]
start <- which(COP_close$COP_Close - COP_close$Y >= 3.5)[2:4]
start_day <- as.numeric(1:nrow(COP_close) %in% start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[
  which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "2008-09-26"), ]
m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_Sept_08
```

```{r}
m_COP_Sept_08_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_Sept_08_no
```

<!-- In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs. It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt [Source](https://www.marketwatch.com/story/lehman-folds-with-record-613-billion-debt).

```{r}
COP_close <- COP_close %>% select(-"start_day")
#start <- which(COP_close$Date == "2008-09-08")
start <- which(COP_close$Date == "2008-09-12")

## change to equality
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_9_08_08_1 <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1 #-6.95 (1.98) in 2020 dollars
```

```{r}
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_08_08_1_no <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1_no #-6.94 (1.94) in 2020 dollars
```
-->

@@

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2014-11-26")
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
alpha_11_27_14
```

@@

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
## change to equality
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
```

@@

```{r}

a_estimates <- rbind( c(alpha_9_11, alpha_9_11_no),
  c(alpha_3_18, alpha_3_18_no),
  c(alpha_Sept_08, alpha_Sept_08_no),
  c(alpha_11_27_14, alpha_11_27_14_no))
colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no")
rownames(a_estimates) <- c("y2001", "my2008", "sy2008", "y2014")
```

@@

```{r}
a_adj <- colMeans(a_estimates[, c(1,3)])
a_adj_no911 <- colMeans(a_estimates[-1, c(1,3)])
weights <- rbind(
(1 / a_estimates[, c(2,4)])[1, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[2, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[3, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[, c(2,4)])
)
a_adj_IVW <- colSums(weights * a_estimates[, c(1,3)])
weights_no911 <- rbind(
(1 / a_estimates[-1, c(2,4)])[1, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[2, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)])
)
a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1, c(1,3)])
```

@@

```{r}
additive <- colMeans(a_estimates[c(2,3), c(1,3)]) + a_estimates[4, c(1,3)]
additive
```

@@

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
#start_day <- as.numeric(1:nrow(COP_close) >= start)
#COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
```

>>>>

```{r}
## September 11th (no trading from T-F); 1 day nowcast
COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
GSPC_close <- GSPC %>% dplyr::select(GSPC.Close, Date) %>% 
  rename(GSPC_Close = GSPC.Close)
COP_close <- merge(COP_close, GSPC_close)
COP_close <- merge(COP_close, WTI_Crude)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start <- which(COP_close$Date == "2001-09-10")
start_day <- as.numeric(1:nrow(COP_close) == start + 1)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
alpha_9_11
```

@@

The first 4 major shocks of 2008 were proceeded by unprecedented failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike. The September 12th and September 26th shock effects were proceeded by the bailouts or failures of Lehman Brothers and Washington Mutual financial institutions. The September 8th shock effect was proceeded by Fannie Mae and Freddie Mac being placed in conservatorship.

```{r}
#COP_close <- COP_close %>% dplyr::select(-"start_day")
COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
COP_close <- merge(COP_close, GSPC_close)
COP_close <- merge(COP_close, WTI_Crude)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start_09_08_08 <- which(COP_close$Date == "2008-09-08")
start_09_12_08 <- which(COP_close$Date == "2008-09-12")
start_09_26_08 <- which(COP_close$Date == "2008-09-26")
start_day_09_08_08 <- as.numeric(1:nrow(COP_close) %in% start_09_08_08)
start_day_09_12_08 <- as.numeric(1:nrow(COP_close) %in% start_09_12_08)
start_day_09_26_08 <- as.numeric(1:nrow(COP_close) %in% start_09_26_08)
COP_close <- COP_close %>% mutate(start_day_09_08_08 = start_day_09_08_08, 
                                  start_day_09_12_08 = start_day_09_12_08, 
                                  start_day_09_26_08 = start_day_09_26_08)
COP_close_small <- COP_close[
  which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "2008-09-26"), ]
m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day_09_08_08 + start_day_09_12_08 + 
                      start_day_09_26_08 + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3:5,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_Sept_08
```

@@

```{r}
m_COP_Sept_08_no <- lm(Y ~ COP_Close + start_day_09_08_08 + start_day_09_12_08 + 
                      start_day_09_26_08, data = COP_close_small)
alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3:5,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_Sept_08_no
```

@@

```{r}
COP_close <- COP %>% dplyr::select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
COP_close <- merge(COP_close, GSPC_close)
COP_close <- merge(COP_close, WTI_Crude)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start <- which(COP_close$Date == "2014-11-26")
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
alpha_11_27_14
```

@@

```{r}
COP_close <- COP_close %>% dplyr::select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
## change to equality
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
```

@@

```{r}
a_estimates <- rbind( c(alpha_9_11, alpha_9_11_no),
  cbind(alpha_Sept_08, alpha_Sept_08_no),
  c(alpha_11_27_14, alpha_11_27_14_no))
colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no")
rownames(a_estimates) <- c("y2001","s8y2008","s12y2008","s26y2008","y2014")
```

@@

```{r}
a_adj <- colMeans(a_estimates[, c(1,3)])
a_adj_no911 <- colMeans(a_estimates[-1, c(1,3)])
weights <- rbind(
(1 / a_estimates[, c(2,4)])[1, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[2, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[3, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[5, ] / colSums(1 / a_estimates[, c(2,4)])
)
a_adj_IVW <- colSums(weights * a_estimates[, c(1,3)])
weights_no911 <- rbind(
(1 / a_estimates[-1, c(2,4)])[1, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[2, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[4, ] / colSums(1 / a_estimates[-1, c(2,4)])
)
a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1, c(1,3)])
```

@@

```{r}
additive <- colMeans(a_estimates[2:4, c(1,3)]) + a_estimates[4, c(1,3)]
additive
```

@@

```{r}
COP_close <- COP_close %>% dplyr::select(-"start_day")
start <- which(COP_close$Date == "2020-03-06")
#start_day <- as.numeric(1:nrow(COP_close) >= start)
#COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
```
